Graphical representation example: Alternative interpretations

### 2023-11-23 notebooks/Graphical_representation_alternatives.Rmd
Adds item table output selection
Versions chunks with original plot output in the test space

>>>>

```{r example-items-obl-out}
```
```{r compose-oblique-plot-latent-space}
plot_oblique <- items_oblique |>
  arrange(desc(item))         |> # To plot them in reverse order
  ggplot(
    aes(
      origin_transf_1, origin_transf_2,
      xend  = end_transf_1, yend = end_transf_2,
      color = item, fill = item
    ),
  )                                                         +
  geom_segment(
    arrow     = arrow(angle = 20, length = unit(10, "points"), type = "closed"),
    linejoin  = "mitre",
    linewidth = VECTOR_WIDTH
  )                                                         +
  scale_x_continuous(
    limits       = c(-2, 3),
    breaks       = (0:4) - 2 / CORR_ARC_TAN,
    labels       = 0:4,
    minor_breaks = NULL,
    name         = NULL,
    oob          = oob_keep
  )                                                         +
  scale_y_continuous(
    limits       = c(-2, 2.8),
    breaks       = -3:3 * cos(CORR_VALUE),
    labels       = function(x) x / cos(CORR_VALUE),
    minor_breaks = 0,
    name         = NULL,
    oob          = oob_keep
  )                                                         +
  geom_abline(slope = CORR_ARC_TAN, linewidth = LINE_WIDTH) +
  coord_fixed(expand = FALSE, clip = "on")                  +
  scale_color_manual(values = PALETTE)                +
  geom_abline(
    slope     =  CORR_ARC_TAN,
    intercept = -CORR_ARC_TAN * (-4:4),
    linewidth = LINE_WIDTH,
    linetype  = "17"
  )                                                         +
  geom_hline(yintercept = 0, linewidth = LINE_WIDTH)        +
  theme(
    axis.line          = element_blank(),
    panel.grid.major.y = element_line(
      color     = "black",
      linewidth = LINE_WIDTH,
      linetype  = "17"
    )
  )
```

```{r item-plot-latent-space-out}
#| fig.cap: |
#|   Item plots in an oblique, orthonormal latent space (with correlation = .5)
plot_oblique
```
